Supplememtary examples for:

### 2020-06-15 extensions.Rmd
Remove the scripthooks and the python code for symbolic algebra

library( formatR)
library( knitr)
library( lavaan)

# ----- Script hook for printing only certain lines

hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
   lines <- options$output.lines
   if (is.null(lines)) {
     return(hook_output(x, options))  # pass to default hook
   }
   x <- unlist(strsplit(x, "\n"))
   more <- "..."
   if (length(lines)==1) {        # first n lines
     if (length(x) > lines) {
       # truncate the output, but add ....
       x <- c(head(x, lines), more)
     }
   } else {
     x <- c(if (abs(lines[1])>1) more else NULL, 
            x[lines], 
            if (length(x)>lines[abs(length(lines))]) more else NULL
           )
   }
   # paste these lines together
   x <- paste(c(x, ""), collapse = "\n")
   hook_output(x, options)
})

# From: https://community.rstudio.com/t/showing-only-the-first-few-lines-of-the-results-of-a-code-chunk/6963/2
# Retrieved on: 26.05.2020

# ----- Script hook to increase space between text and chunk output

hook_output_def = knitr::knit_hooks$get('output')
knitr::knit_hooks$set(output = function(x, options) {
  if (!is.null(options$vspaceout)) {
    end <- paste0("\\vspace{", options$vspaceout, "}")
    stringr::str_c(hook_output_def(x, options), end)
  } else {
    hook_output_def(x, options)
  }
})

hook_source_def = knitr::knit_hooks$get('source')
knitr::knit_hooks$set(source = function(x, options) {
  if (!is.null(options$vspaceecho)) {
    begin <- paste0("\\vspace{", options$vspaceecho, "}")
    stringr::str_c(begin, hook_source_def(x, options))
  } else {
    hook_source_def(x, options)
  }
})

# From: https://stackoverflow.com/questions/43379224/add-vertical-space-above-and-below-figures-code-chunks
# Retrieved on: 04.06.2020
```

@@

```{python, results='asis', eval=FALSE, echo=FALSE}
# Following sympy code double-checks how to specify this model 
# using matrix algebra. Turn eval=TRUE to see the vector y.

from sympy import *

x1, x2, x3, y1, y2, y3, d1, d2, d3, e1, e2, e3, xi1, xi2, xi3, n1, n2, n3, a, z1, z2, z3, b, x11, x21, x31, x12, x22, x32, x13, x23, x33, xi1, xi2, xi3, d11, d21, d31, d12, d22, d32, d13, d23, d33, l21, l31, l22, l32, l23, l33 = symbols('x1, x2, x3, y1, y2, y3, delta1, delta2, delta3, varepsilon1, varepsilon2, varepsilon3, xi1, xi2, xi3, eta1, eta2, eta3, alpha, zeta1, zeta2, zeta3, beta, x11, x21, x31, x12, x22, x32, x13, x23, x33, xi1, xi2, xi3, delta11, delta21, delta31, delta12, delta22, delta32, delta13, delta23, delta33, lambda21, lambda31, lambda22, lambda32, lambda23, lambda33')

y = Matrix([[y1],[y2],[y3],[x11],[x21],[x31],[x12],[x22],[x32],[x13],[x23],[x33]])
Ly = Matrix([[1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0, 0],
             [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, 0, 0]])
n = Matrix([[y1],[y2],[y3],[x11],[x21],[x31],[x12],[x22],[x32],[x13],[x23],[x33],[a],[xi1],[xi2],[xi3]])
B = Matrix([[0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, b, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, b, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0, b],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, l21, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, l31, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, l22, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, l32, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 1],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, l23],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, l33],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0],
            [0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0, 0]])
z = Matrix([[e1],[e2],[e3],[d11],[d21],[d31],[d12],[d22],[d32],[d13],[d23],[d33],[a],[xi1],[xi2],[xi3]])
I = eye(16)

print('$' + latex(Ly*Inverse(I - B)*z) + '$')
```

>>>>

library( formatR)
library( knitr)
library( lavaan)
```

```{r, code=readLines("scripthooks.R"), echo=FALSE, results=FALSE}
```

@@
